---
title: "TS Project (Spring 24)"
author: "Linda Ji"
date: "2024-05-19"
output: html_document
---

---
#
add new chunks with cmd+opt+i
#add <- with opt+-

```{r}
#install.packages("plotly")
#install.packages("devtools")
#devtools::install_github("hrbrmstr/AnomalyDetection")
library(forecast)
library(lmtest)
library(urca)
library(tseries)
library(xts)
library(boot)
library(arfima)
library(fracdiff)
library(repr)
library(TSA)
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(caret)
library(tidyverse)
library(doParallel)
library(lattice)
library(pdp)
library(nnfor)
library(anomalize)
library(AnomalyDetection)
library(hrbrthemes)
library(plotly)

options(repr.plot.width=15, repr.plot.height=6)
options(warn=-1)
```
# 1. Problem statement:
- To build a model that more accurately predicts the unit sales for thousands of items sold at top three Corporación Favorita stores. ( After EDA, store number 44, 45, & 47 as top best performing sales)
(a large Ecuadorian-based grocery retailer)
- Forecast the sales data for each outlet from 2017-08-02 to to 2017-08-15 given data from  2013-01-01 to 2017-08-01
- Evaluation metric: Root Mean Squared Error

Load data
```{r}
datapath <- "/Users/lindaji/Downloads/02 Time Series/00 Project/retail_data"
sales <- read.csv(paste(datapath,"train.csv",sep="/"),header=T)
oil <- read.csv(paste(datapath,"oil.csv",sep="/"),header=T)
holiday <- read.csv(paste(datapath,"holidays_events.csv",sep="/"),header=T)
store <- read.csv(paste(datapath,"stores.csv",sep="/"),header=T)
head(oil)
tail(oil)
head(sales)
```
# 02. Assumptions/Hypotheses about data and/or modeling
- Assume sales data is seasonal, to test which are the significant seasonal cycles
- Assume forecasted sales will have the same trend as train test set 
- Assume that when data is forecast on a store level( by aggregating family of products) the seasonality pattern might change somewhat, but we are still able to model it. 

# 03. Data properties 
(stationarity, correlations, data distribution) and Exploratory data, 
- please refer to python file for EDA, stationarity & correlation check done there.

```{r}
sales$family %>% table() %>% as.data.frame()
a <- sales %>% group_by(family) %>% summarise(mean_sales = round(mean(sales, na.rm=TRUE),2),
                                              median_sales = round(median(sales, na.rm = TRUE),2),
                                              IQR_sales = IQR(sales),
                                              max_sales = max(sales),
                                              total_sales = sum(sales))%>%
  arrange(desc(total_sales))
#a

# Define a maroon color palette
maroon_palette <- c("#800000", "#A52A2A", "#B22222", "#8B0000", "#CD5C5C", "#E9967A")

# Ensure the palette is long enough for the number of families
num_families <- length(unique(a$family))
maroon_palette <- rep(maroon_palette, length.out = num_families)

b <- ggplot(a)+
    geom_col(aes(x = reorder(family, -mean_sales), y = mean_sales, fill = str_to_title(family)))+
    scale_fill_viridis_d()+
    #scale_fill_manual(values = maroon_palette) +
    theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
    labs(title = 'Proportion of sales by product family (rollover to see labels)',
         x = 'Product family',
         y = 'Average daily sales',
         legend = 'Family')

ggplotly(b, width = 800, height = 450)

sales %>% 
  filter(sales>0) %>% 
  group_by(date) %>% 
  summarise(avg_sales_per_day = mean(sales, na.rm=TRUE)) %>% 
  right_join(oil, by='date') %>% 
  ggplot()+
    geom_line(aes(x = date, y = scale(dcoilwtico), colour = 'Oil_price'), na.rm = TRUE)+
    geom_line(aes(x = date, y = scale(avg_sales_per_day), colour = 'Sales'), na.rm = TRUE)+
  labs(title = "Total store sales compared to local oil prices: 2013-2017",
       subtitle = "Data has been normalised for comparrison")
```


# 04. Feature engineering
## A.) Combine data in train & oil
```{r}
# Make a list of dates to join oil prices with (as it is missing weekends)
unq_dates <- expand.grid(date = unique(sales$date))
oil$date <- as.Date(oil$date)
unq_dates$date <- as.Date(unq_dates$date)
sales$date <- as.Date(sales$date)
all_oil <- left_join(unq_dates, oil, by = "date")
#all_oil

# Interpolate NA values in a new 'oil_price' column
all_oil$oil_price <- c(na.approx(all_oil$dcoilwtico), NA)

# Assign the interpolated oil prices to the sales dataset

sales_oil <- left_join(sales, all_oil, by = "date")

# Drop id, dcoilwtico
to_drop <- c("id", "dcoilwtico","promotion")
sales_oil <- sales_oil[, !names(sales_oil) %in% to_drop]

# Replace missing values in onpromotion with 0
sales_oil$onpromotion[is.na(sales_oil$onpromotion)] <- 0

# Change promotion column to 1 if there is a promotion number
sales_oil$onpromotion <- if_else(sales_oil$onpromotion != 0, 1, sales_oil$onpromotion)

head(sales_oil)
#View(sales_oil)
```
### Check Store information
```{r}
store_3 <- subset(store,store_nbr %in% c(44,45,47))
#store_3
```

## B.) Add local holiday and national columns
```{r}
holiday$date <- as.Date(holiday$date)

#Filter for local holidays only relevant to Quito, and only holidays that were not transferred
holiday_local <- subset(holiday,locale_name=="Quito")
holiday_local <- subset(holiday_local,transferred=="False")
holiday_local$local_holiday <- rep(1, nrow(holiday_local)) # add dummy variable 1 
holiday_local_2 <- select(holiday_local,date, local_holiday)
print(head(holiday_local_2))

#filter for national holidays and holidays that were not transferred
holiday_national <- subset(holiday,locale=="National")
holiday_national <- subset(holiday_national,transferred=="False")
holiday_national$national_holiday <- rep(1, nrow(holiday_national))
holiday_national_2 <- select(holiday_national,date, national_holiday)
print(head(holiday_national_2))

sales_oil <- left_join(sales_oil, holiday_local_2, by = "date")
sales_oil <- left_join(sales_oil, holiday_national_2, by = "date",relationship = "many-to-many")

sales_oil$local_holiday <- na.fill(sales_oil$local_holiday, fill = 0)
sales_oil$national_holiday <- na.fill(sales_oil$national_holiday, fill = 0)
sales_oil$sales <- na.fill(sales_oil$sales, fill = 0)
print(head(sales_oil))
```
## C.) Subset to top 3 stores(store number 44, 45, 47 only)

```{r}
sales_44 <- subset(sales_oil,store_nbr %in% c(44))
sales_45 <- subset(sales_oil,store_nbr %in% c(45))
sales_47 <- subset(sales_oil,store_nbr %in% c(47))
#sales_44
```
# 05. Data processing 
(anomaly detection, cleansing and imputations) and transformations
## D.) Aggregated & impute data for each store 
```{r}
sales_44a <- sales_44 %>%
  group_by(date) %>%
  summarise(sales = sum(sales))

sales_45a <- sales_45 %>%
  group_by(date) %>%
  summarise(sales = sum(sales),oil_price=mean(oil_price),local_holiday=mean(local_holiday),national_holiday=mean(national_holiday))

sales_47a <- sales_47 %>%
  group_by(date) %>%
  summarise(sales = sum(sales),oil_price=mean(oil_price),local_holiday=mean(local_holiday),national_holiday=mean(national_holiday))
print(head(sales_47a))
```
## Check May-Jun 2016 plot for pulse, 
as that's when earthquake relief donation efforts might have increased sales more than usual
```{r}
#earthquake_start_date <- as.Date("2015-01-01")
#earthquake_end_date <- as.Date("2016-12-01")
#clean_train_44_eq <- clean_train_44 %>% 
  #filter(date < earthquake_end_date)%>% 
  #filter(date > earthquake_start_date)

#autoplot(ts(clean_train_44_eq$sales_i,start=c(2015,01,01),frequency=365.25))

```

## E.) Imput sales for 0 values 
- There are zero sales on 1st day of each year as the stores are closed
```{r}
lm_model_44 <- lm(sales ~ date, data = sales_44a)
sales_44a$sales_i <- ifelse(is.na(sales_44a$sales) | sales_44a$sales == 0, predict(lm_model_44, newdata = sales_44a), sales_44a$sales)

lm_model_45 <- lm(sales ~ date, data = sales_45a)
sales_45a$sales_i <- ifelse(is.na(sales_45a$sales) | sales_45a$sales == 0, predict(lm_model_45, newdata = sales_45a), sales_44a$sales)

lm_model_47 <- lm(sales ~ date, data = sales_44a)
sales_47a$sales_i <- ifelse(is.na(sales_47a$sales) | sales_47a$sales == 0, predict(lm_model_47, newdata = sales_47a), sales_47a$sales)

#sales_44a$sales <- as.numeric(sales_44a$sales)
#sales_45a$sales <- as.numeric(sales_45a$sales)
#sales_47a$sales <- as.numeric(sales_47a$sales)
#sales_47a

autoplot(ts(sales_44a$sales_i))
autoplot(ts(sales_45a$sales_i))
autoplot(ts(sales_47a$sales_i))
#sales_47a$sales_i
```
## F.) Filter outliers and impute ( higher values in 2016 due to earthquake relief efforts etc. )
```{r}
# Detect outliers
outliers44 <- tsoutliers(sales_44a$sales_i, iterate = 2, lambda = NULL)
outliers45 <- tsoutliers(sales_45a$sales_i, iterate = 2, lambda = NULL)
outliers47 <- tsoutliers(sales_47a$sales_i, iterate = 2, lambda = NULL)
print(outliers44)
print(outliers45)
print(outliers47)
# Replace outliers in sales_44a$sales_i with the replacements
sales_44a$sales_i[outliers44$index] <- outliers44$replacements
sales_45a$sales_i[outliers45$index] <- outliers45$replacements
sales_47a$sales_i[outliers47$index] <- outliers47$replacements

#Plot to check
plot(ts(sales_44a,start=2013,frequency=365.25))
autoplot(ts(sales_45a$sales_i))
autoplot(ts(sales_47a$sales_i))
```
## G.) Clean data: split train test
```{r}
cutoff_date <- as.Date("2017-08-02")
clean_train_44 <- sales_44a %>% filter(date < cutoff_date)
clean_test_44 <- sales_44a %>% filter(date >= cutoff_date)
clean_train_45 <- sales_45a %>% filter(date < cutoff_date)
clean_test_45 <- sales_45a %>% filter(date >= cutoff_date)
clean_train_47 <- sales_47a %>% filter(date < cutoff_date)
clean_test_47 <- sales_47a %>% filter(date >= cutoff_date)
clean_train_47
```

## H.) Raw data: Split Train test 
- For checking difference in evaluation metrics
```{r}
#Split for raw data (missing values and anomalies not imputed)
sales_grouped <- sales %>%
    group_by(store_nbr) %>%
    summarise(total_daily_sales = sum(sales))
sales_grouped
sales
# Determine the cutoff date for splitting
cutoff_date <- as.Date("2017-08-02")
cutoff_date2 <- as.Date("2016-08-02")
# Split the data into training and testing sets based on the cutoff date
train <- sales %>% filter(date < cutoff_date)
#train <- sales %>% filter(date < cutoff_date)%>% filter(date >= cutoff_date2)
test <- sales %>% filter(date >= cutoff_date)

# Split by store: 
train_44 <- subset(train,store_nbr=="44")
train_45 <- subset(train,store_nbr=="45")
train_47 <- subset(train,store_nbr=="47")

test_44 <- subset(test,store_nbr=="44")
test_45 <- subset(test,store_nbr=="45")
test_47 <- subset(test,store_nbr=="47")

# Test on sub families
train_44_grocery <- subset(train_44,family=="GROCERY I")%>% select(date, sales)
test_44_grocery <- subset(test_44,family=="GROCERY I")%>% select(date, sales)
train_44_grocery
test_44_grocery
```
Aggregate the total daily sales
```{r}
train_44_agg <- train_44 %>%
  group_by(date) %>%
  summarise(total_daily_sales = sum(sales),store_nbr=mean(store_nbr))
train_45_agg <- train_45 %>%
  group_by(date) %>%
  summarise(total_daily_sales = sum(sales),,store_nbr=mean(store_nbr))
train_47_agg <- train_47 %>%
  group_by(date) %>%
  summarise(total_daily_sales = sum(sales),store_nbr=mean(store_nbr))
test_44_agg <- test_44 %>%
  group_by(date) %>%
  summarise(total_daily_sales = sum(sales),store_nbr=mean(store_nbr))
test_45_agg <- test_45 %>%
  group_by(date) %>%
  summarise(total_daily_sales = sum(sales),store_nbr=mean(store_nbr))
test_47_agg <- test_47 %>%
  group_by(date) %>%
  summarise(total_daily_sales = sum(sales),store_nbr=mean(store_nbr))
head(test_44_agg)
plot(ts(train_44_agg$total_daily_sales,start=2013,frequency=365.25))
```

## I.) Plot Time Series (without imputations or outlier replacement)
```{r}
options(repr.plot.width = 28, repr.plot.height = 7)
# Merge the datasets by row
merged_dataset <- rbind(train_44_agg, train_45_agg, train_47_agg)
merged_dataset <- merged_dataset %>% mutate(store_nbr = as.factor(store_nbr))

library(lubridate)

# Aggregate by month
data_store_44_monthly <- merged_dataset %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month,store_nbr) %>%
  summarise(total_monthly_sales = sum(total_daily_sales))

ggplot(merged_dataset, aes(x = date, y = total_daily_sales, color = store_nbr))+
  geom_line() +
  labs(x = "Date", y = "Total Daily Sales", title = "Sales Over Time") +
  #scale_color_manual(values = c("red", "blue", "green"))
  theme_minimal()

ggplot(data_store_44_monthly, aes(x = month, y = total_monthly_sales, color = store_nbr))+
  geom_line() +
  labs(x = "Date", y = "Total Monthly Sales", title = "Sales Over Time") +
  scale_color_manual(values = c("red", "blue", "green"))


```

# Anomaly detection package
No anmalies detected
```{r}
# Create a timestamp sequence based on the frequency
timestamps <- as.Date(train_44_agg$date)

# Create a data frame with timestamps and total_daily_sales
ts_44 <- data.frame(timestamp = timestamps, sales = clean_train_44$sales_i)

res <- ad_ts(ts_44, max_anoms=0.2, direction='both',threshold='med_max')

glimpse(res)
```


## J). Testing Family level Seasonality
```{r}
library(ModelMetrics)
# Test for family 
plot(ts(train_44_grocery))

# Check if there is seasonal pattern Year over Year
YoY <- train_44_grocery %>% group_by(date=floor_date(date, "year")) %>% summarize(sales=mean(sales))
acf(YoY$sales) # No significant yearly trend

# Check if there is seasonal pattern Quarter over Quarter
QoQ <- train_44_grocery %>% group_by(date=floor_date(date, "quarter")) %>% summarize(sales=mean(sales))
acf(QoQ$sales) # No significant quarterly trend

# Check if there is seasonal pattern Month over month
MoM <- train_44_grocery %>% group_by(date=floor_date(date, "month")) %>% summarize(sales=mean(sales))
acf(MoM$sales) # significant monthly trend

# Check if there is seasonal pattern Week over Week
WoW <- train_44_grocery %>% group_by(date=floor_date(date, "week")) %>% summarize(sales=mean(sales))
acf(WoW$sales) # very significant weekly trend

# Check if there is seasonal pattern Day over Day
DoD <- train_44_grocery  %>% group_by(date=floor_date(date, "day")) %>% summarize(sales=mean(sales))
acf(DoD$sales) # very significant daily trend


tbats44_grocery <- tbats(ts(train_44_grocery$sales),seasonal.periods=c(7,365.25))
tbats44_grocery
#plot(tbats44_grocery)
predict44_grocery <- predict(tbats44_grocery,h=14)
#plot(predict44_grocery)
(rmse44_g <- rmse(test_44_grocery$sales, predict44_grocery$mean))
```
### Plot the family predicted graph
Family level prediction for RMSE showed 38,830, much bigger than around 10,000 for store level prediction, so will continue with store level modeling
```{r}
library(ggplot2)
train_44_grocery_predicted <- test_44_grocery
train_44_grocery_predicted$sales <- as.numeric(predict44_grocery$mean)

# plot the graph
ggplot(data=train_44_grocery) +
  geom_line(data=test_44_grocery, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_44_grocery_predicted, aes(x=date, y=sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))
```

# K.) Checking Store level seasonality
- Very significant weekly and daily seasonality in acf graph
```{r}

# Check if there is seasonal pattern Year over Year
YoY <- train_44_agg %>% group_by(date=floor_date(date, "year")) %>% summarize(sales=mean(total_daily_sales))
acf(YoY$sales) # No significant yearly trend

# Check if there is seasonal pattern Quarter over Quarter
QoQ <- train_44_agg %>% group_by(date=floor_date(date, "quarter")) %>% summarize(sales=mean(total_daily_sales))
acf(QoQ$sales) # No significant quarterly trend

# Check if there is seasonal pattern Month over month
MoM <- train_44_agg %>% group_by(date=floor_date(date, "month")) %>% summarize(sales=mean(total_daily_sales))
acf(MoM$sales) # significant monthly trend

# Check if there is seasonal pattern Week over Week
WoW <- train_44_agg %>% group_by(date=floor_date(date, "week")) %>% summarize(sales=mean(total_daily_sales))
acf(WoW$sales) # very significant weekly trend

# Check if there is seasonal pattern Day over Day
DoD <- train_44_agg  %>% group_by(date=floor_date(date, "day")) %>% summarize(sales=mean(total_daily_sales))
acf(DoD$sales) # very significant daily trend
```
# 06. Proposed approaches (model) with justification and trade-offs, if any
## A.) Running TBATs model for both raw aggregated data & cleaned data
- Ideal is to check the difference the data quality makes to the accuracy of the model 
```{r}
#TBATS with raw data
tbats44 <- tbats(ts(train_44_agg$total_daily_sales,start=2013),seasonal.periods=c(7,365.25))
tbats45 <- tbats(ts(train_45_agg$total_daily_sales,start=2013),seasonal.periods=c(7,365.25))
tbats47 <- tbats(ts(train_47_agg$total_daily_sales,start=2013),seasonal.periods=c(7,365.25))
#TBATS with 0 values imputed with linear regression
tbats44_clean <- tbats(ts(clean_train_44$sales,start=2013),seasonal.periods=c(7,365.25))
tbats45_clean <- tbats(ts(clean_train_45$sales,start=2013),seasonal.periods=c(7,365.25))
tbats47_clean <- tbats(ts(clean_train_47$sales,start=2013),seasonal.periods=c(7,365.25))

#TBATS with 0 values imputed with linear regression & anomalies replaced
tbats44_cleana <- tbats(ts(clean_train_44$sales_i,start=2013),seasonal.periods=c(7*12,365.25))
tbats45_cleana <- tbats(ts(clean_train_45$sales_i,start=2013),seasonal.periods=c(7*12,365.25))
tbats47_cleana <- tbats(ts(clean_train_47$sales_i,start=2013),seasonal.periods=c(7*12,365.25))

tbats44_cleana
```

## B.) Checking components of TBAT model
```{r}
comp1 <- tbats.components(tbats44)
plot(comp1)
comp2 <- tbats.components(tbats44_clean)
plot(comp2)
comp3 <- tbats.components(tbats44_cleana)
plot(comp3)
```
## C.) Predicting & Calculating RMSE, using TBATS model 
```{r}
library(ModelMetrics)
#plot(tbats44_grocery)
predict44 <- predict(tbats44,h=14)
predict45 <- predict(tbats45,h=14)
predict47 <- predict(tbats47,h=14)

predict44c <- predict(tbats44_clean,h=14)
predict45c <- predict(tbats45_clean,h=14)
predict47c <- predict(tbats47_clean,h=14)

predict44ca <- predict(tbats44_cleana,h=14)
predict45ca <- predict(tbats45_cleana,h=14)
predict47ca <- predict(tbats47_cleana,h=14)

rmse44 <- rmse(test_44_agg$total_daily_sales, predict44$mean)
rmse45 <- rmse(test_45_agg$total_daily_sales, predict45$mean)
rmse47 <- rmse(test_47_agg$total_daily_sales, predict47$mean)

rmse44c <- rmse(clean_test_44$sales, predict44c$mean)
rmse45c <- rmse(clean_test_45$sales, predict45c$mean)
rmse47c <- rmse(clean_test_47$sales, predict47c$mean)

rmse44ca <- rmse(clean_test_44$sales_i, predict44ca$mean)
rmse45ca <- rmse(clean_test_45$sales_i, predict45ca$mean)
rmse47ca <- rmse(clean_test_47$sales_i, predict47ca$mean)


print(paste("RMSE of store 44:", rmse44))
print(paste("RMSE of store 45:", rmse45))
print(paste("RMSE of store 47:", rmse47))
print(paste("RMSE of store 44_c:", rmse44c))
print(paste("RMSE of store 45_c:", rmse45c))
print(paste("RMSE of store 47_c:", rmse47c))
print(paste("RMSE of store 44_ca:", rmse44ca))
print(paste("RMSE of store 45_ca:", rmse45ca))
print(paste("RMSE of store 47_ca:", rmse47ca))

# Add date column for plotting
train_44_predicted <- test_44_agg
train_44_predicted$total_daily_sales <- as.numeric(predict44$mean)
train_45_predicted <- test_45_agg
train_45_predicted$total_daily_sales <- as.numeric(predict45$mean)
train_47_predicted <- test_47_agg
train_47_predicted$total_daily_sales <- as.numeric(predict47$mean)

train_44_predictedc <- clean_test_44
train_44_predictedc$sales <- as.numeric(predict44c$mean)
train_45_predictedc <- clean_test_45
train_45_predictedc$sales <- as.numeric(predict45c$mean)
train_47_predictedc <- clean_test_47
train_47_predictedc$sales <- as.numeric(predict47c$mean)

train_44_predictedca <- clean_test_44
train_44_predictedca$sales_i <- as.numeric(predict44ca$mean)
train_45_predictedca <- clean_test_45
train_45_predictedca$sales_i <- as.numeric(predict45ca$mean)
train_47_predictedca <- clean_test_47
train_47_predictedca$sales_i <- as.numeric(predict47ca$mean)

checkresiduals(predict44)
checkresiduals(predict44c)
checkresiduals(predict44ca)
```

```{r}
library(dplyr)
# Create a dataframe to store the RMSE values
rmse_df <- data.frame(Store = character(),
                      TBATS_RMSE = numeric(),
                      stringsAsFactors = FALSE)


# Append RMSE values for each store and model
rmse_df <- rbind(rmse_df, data.frame(Store = "Store_44", TBATS_RMSE = rmse44))
rmse_df <- rbind(rmse_df, data.frame(Store = "Store_45", TBATS_RMSE = rmse45))
rmse_df <- rbind(rmse_df, data.frame(Store = "Store_47", TBATS_RMSE = rmse47))

TBATS_RMSE_0_filled<- c(rmse44c,rmse45c,rmse47c)
TBATS_RMSE_0_filled_anomalies_removed<- c(rmse44ca,rmse45ca,rmse47ca)
rmse_df <- cbind(rmse_df, TBATS_RMSE_0_filled = TBATS_RMSE_0_filled,TBATS_RMSE_0_filled_anomalies_removed=TBATS_RMSE_0_filled_anomalies_removed)
print(rmse_df)


# Calculate the mean of each column
summarise_df <- rmse_df %>%
  summarise(TBATS_RMSE = sum(TBATS_RMSE),TBATS_RMSE_0_filled = sum(TBATS_RMSE_0_filled),TBATS_RMSE_0_filled_anomalies_removed = sum(TBATS_RMSE_0_filled_anomalies_removed))

sales_44a <- sales_44 %>%
  group_by(date) %>%
  summarise(sales = sum(sales))

# View the mean data
print(summarise_df)

```

## Plot the store predicted graph for raw data
```{r}
# plot the graph
ggplot(data=train_44_agg) +
  geom_line(data=test_44_agg, aes(x=date, y=total_daily_sales, group=1, col='r')) +
  geom_line(data=train_44_predicted, aes(x=date, y=total_daily_sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

ggplot(data=train_45_agg) +
  geom_line(data=test_45_agg, aes(x=date, y=total_daily_sales, group=1, col='r')) +
  geom_line(data=train_45_predicted, aes(x=date, y=total_daily_sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

ggplot(data=train_47_agg) +
  geom_line(data=test_47_agg, aes(x=date, y=total_daily_sales, group=1, col='r')) +
  geom_line(data=train_47_predicted, aes(x=date, y=total_daily_sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

```
# Plot for cleaned data
```{r}
# plot the graph
ggplot(data=clean_train_44) +
  geom_line(data=clean_test_44, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_44_predictedc, aes(x=date, y=sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

ggplot(data=clean_train_45) +
  geom_line(data=clean_test_45, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_45_predictedc, aes(x=date, y=sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

ggplot(data=clean_train_47) +
  geom_line(data=clean_test_47, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_47_predictedc, aes(x=date, y=sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

# plot the graph
ggplot(data=clean_train_44) +
  geom_line(data=clean_test_44, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_44_predictedca, aes(x=date, y=sales_i, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

ggplot(data=clean_train_45) +
  geom_line(data=clean_test_45, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_45_predictedca, aes(x=date, y=sales_i, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

ggplot(data=clean_train_47) +
  geom_line(data=clean_test_47, aes(x=date, y=sales, group=1, col='r')) +
  geom_line(data=train_47_predictedca, aes(x=date, y=sales_i, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))
```
## D.) Testing Store level auto arima model 
```{r}
library(forecast)
aa44 <- auto.arima(train_44_agg$total_daily_sales)
aa45 <- auto.arima(train_45_agg$total_daily_sales)
aa47 <- auto.arima(train_47_agg$total_daily_sales)
aa44
```
### RMSE for autoarima
```{r}
library(ModelMetrics)
forecast_aa44 <- forecast(aa44,14)
forecast_aa45 <- forecast(aa45,14)
forecast_aa47 <- forecast(aa47,14)
plot(forecast_aa44)
rmse44_2 <- rmse(test_44_agg$total_daily_sales,forecast_aa44$mean)
rmse45_2 <- rmse(test_45_agg$total_daily_sales,forecast_aa47$mean)
rmse47_2 <- rmse(test_45_agg$total_daily_sales,forecast_aa47$mean)

autoarima_RMSE<- c(rmse44_2,rmse45_2,rmse47_2)

# Bind the new column to the dataframe df with the name "New_Column"
rmse_df <- cbind(rmse_df, autoarima_RMSE = autoarima_RMSE)

print(rmse_df)
```
## E.) Testing Store level holt winters
```{r}
hw44 <- hw(ts(train_44_agg$total_daily_sales, frequency = 7))
hw45 <- hw(ts(train_45_agg$total_daily_sales, frequency = 7))
hw47 <- hw(ts(train_47_agg$total_daily_sales, frequency = 7))

hw44_forecast <- forecast(hw44, h = 14)
hw45_forecast <- forecast(hw45, h = 14)
hw47_forecast <- forecast(hw47, h = 14)

rmse44_3 <- rmse(test_44_agg$total_daily_sales,hw44_forecast$mean)
rmse45_3 <- rmse(test_45_agg$total_daily_sales,hw45_forecast$mean)
rmse47_3 <- rmse(test_47_agg$total_daily_sales,hw47_forecast$mean)

hw_RMSE<- c(rmse44_3,rmse45_3,rmse47_3)
rmse_df <- cbind(rmse_df, holtwinters_RMSE = hw_RMSE)
print(rmse_df)
#rmse44_3
```
### RMSE & Plot
```{r}
train_44_predicted_3 <- test_44_agg
train_44_predicted_3$total_daily_sales <- as.numeric(hw44_forecast$mean)

ggplot(data=train_44_agg) +
  geom_line(data=test_44_agg, aes(x=date, y=total_daily_sales, group=1, col='r')) +
  geom_line(data=train_44_predicted_3, aes(x=date, y=total_daily_sales, group=1, col='b')) +
  scale_color_discrete(name = 'source', labels = c('actual', 'forecast'))

```
## F.) Testing store level state space model
```{r}

ts_data <- ts(clean_train_44$sales_i, frequency = 365.25,start=2013)
ss_model <- ets(ts_data)
summary(ss_model)

plot(fitted(ss_model))
forecast_values <- forecast(ss_model, h = 14)  
accuracy(forecast_values$mean, clean_test_44$sales_i)
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```